Off the beaten path: \\ Gaia reveals GD-1 stars perturbed off of the main stream track

### 2018-04-30 paper/gd1.tex
Caption

To study the global properties of the stream as a function of stream longitude,
we extract stream stars around a low-order polynomial model for the median
stream latitude, $\phi_2$, as a function of stream longitude, $\phi_1$.
In detail, we find stream ridge points by computing a running median in $\phi_2$
in steps of $2^\circ$ with a window size of $4^\circ$ along $\phi_1$, then fit a
second-order polynomial to the ridge points to find $\phi_{2,
\textrm{track}}(\phi_1)$.
We define the stream as the region within $\left| \phi_2 - \phi_{2,
\textrm{track}}(\phi_1) \right| < 0.75^\circ$.
\figurename~\ref{fig:track-and-model} (top panel) again shows the
high-confidence stream stars, and the two curved lines (blue) show the adopted
upper and lower boundary of the stream region.

We extract properties of the stream from the region defined above as a function
of $\phi_1$ by computing stream properties in overlapping windows:
we set the window size to $4^\circ$ in $\phi_1$, and shift the window center by
$1^\circ$ in longitude for each measurement.
Rows 2--5 in \figurename~\ref{fig:track-and-model} show the background-subtracted
stream surface density, \todo{$\Sigma$?}, the median latitude, $\phi_2$, and median proper motions,
$\mu_{\phi_1}$ and $\mu_{\phi_2}$, extracted in this way, and the associated empirical scatters
(blue lines and shaded regions).
We estimate the local background surface density as an average of areas north and south from the bounded stream region.

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{track_observables.pdf}
\end{center}
\caption{%
\todo{APW}
}
\label{fig:track-and-model}
\end{figure}

>>>>

To study the global properties of the stream as a function of stream longitude,
we extract stream stars around a low-order polynomial model for the median
stream latitude, $\phi_2$, as a function of stream longitude, $\phi_1$.
We find stream ridge points by computing a running median in $\phi_2$ in steps
of $2^\circ$ with a window size of $4^\circ$ along $\phi_1$, then fit a
second-order polynomial to the ridge points to find $\phi_{2,
\textrm{track}}(\phi_1)$.
We then define the stream as the region within $\left| \phi_2 - \phi_{2,
\textrm{track}}(\phi_1) \right| < 0.75^\circ$.
\figurename~\ref{fig:track-and-model} (top panel) again shows the
high-confidence stream stars, and the two curved lines (blue) show the adopted
upper and lower boundary of the stream region.

We extract properties of the stream from the region defined above as a function
of $\phi_1$ by computing median stream properties in overlapping windows:
we set the window size to $3^\circ$ in $\phi_1$, and shift the window center by
$1^\circ$ in longitude for each subsequent measurement.
Panels 3--5 in \figurename~\ref{fig:track-and-model} show the
background-subtracted stream surface density and median proper motion
components, $\mu_{\phi_1}$ and $\mu_{\phi_2}$, extracted in this way (dark
lines), with the associated empirical scatters (shaded regions).
We estimate the local background surface density as an average of areas north
and south of the bounded stream region.

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{track_observables.pdf}
\end{center}
\caption{%
Median stream properties computed from the proper motion and CMD filtered GD-1
stars, and the same for a toy model for the stream track.
\textit{Panel (a)}: Sky positions of candidate GD-1 stars selected using \gaia\
proper motions and \pans\ photometry.
Lines show a 2nd-order polynomial fit to the median stream track offset by $\pm
0.75^\circ$; the region between these lines is adopted as the nomial stream
region.
\textit{Panel (b)}: Sky positions of simulated star particles from a toy mock
stream model of the GD-1 stream track.
\textit{Panel (c)}: Background-subtracted surface-density estimates computed in
running, overlapping $3^\circ$ windows for both GD-1 data and toy model.
\textit{Panel (d)}: Median proper motion along the stream longitude computed in
the same bins as previous panel.
\textit{Panel (e)}: Same as Panel (d), but for proper motion in stream latitude.
}
\label{fig:track-and-model}
\end{figure}
